Determinism, Complexity, and Predictability in Computer Performance

### 2014-08-04 concl.tex
last paragraph

Nonstationarity is a serious challenge in any time-series modeling
problem.  Any regime shift that causes a change in the predictive
structure between the training signal and the test signal, for
instance, will skew the MASE score (and the points on the curve),
obviating the utility of our heuristic.  \alert{Conversely, though,} a
MASE score of a random-walk prediction that is larger than 1---as
mentioned at end of the previous section---could potentially be a good
indicator that a signal is nonstationary.  Detecting regime
shifts---and adapting prediction models accordingly---is an important
area of future work.  Indeed, one of the first applications of
permutation entropy was to recognize the regime shift in brainwave
data that occurs when someone has a seizure~\cite{cao2004det}.  Recall
that the signal in Figure~\ref{fig:svd-ts-colored} was especially
useful for the study in this paper because it contained a number of
different regimes.  We segmented this signal visually, but one could
imagine using permutation entropy to do so instead.  Automating
regime-shift detection would be an important step towards a fully
adaptive modeling strategy, where old models are discarded and new
ones are rebuilt whenever the time series enters a new regime.  WPE
would be particularly powerful in this scenario, as its value can not
only help with regime-shift detection, but also suggest what kind of
model might work well in each new regime.  Of particular interest
would be the class of so-called \emph{hybrid systems}~\cite{hybrid},
which exhibit discrete transitions between different continuous
regimes---e.g., a lathe that has an intermittent instability or
traffic at an internet router, whose characteristic normal traffic
patterns shift radically during an attack.  Effective modeling and
prediction of these kinds of systems is quite difficult; doing so
adaptively and automatically---in the manner that is alluded to at the
end of the previous paragraph---would be an interesting challenge.

>>>>

Nonstationarity is a serious challenge in any time-series modeling
problem.  Any regime shift that causes a change in the predictive
structure between the training signal and the test signal, for
instance, may skew the MASE score and thereby obviate the utility of
our heuristic.  Conversely, though, a MASE score of a random-walk
prediction that is significantly different from 1.0---as mentioned at
end of the previous section---could potentially be a good indicator of
nonstationary.

Detecting regime shifts---and adapting prediction models
accordingly---is an important area of future work.  Indeed, one of the
first applications of permutation entropy was to recognize the regime
shift in brainwave data that occurs when someone has a
seizure~\cite{cao2004det}.  Recall that the signal in
Figure~\ref{fig:svd-ts-colored} was especially useful for the study in
this paper because it contained a number of different regimes.  We
segmented this signal visually, but one could imagine using some
combination of WPE and MASE to do so instead (e.g., in a sliding
window).  Automating regime-shift detection would be an important step
towards a fully adaptive modeling strategy, where old models are
discarded and new ones are rebuilt whenever the time series enters a
new regime.  WPE would be particularly powerful in this scenario, as
its value can not only help with regime-shift detection, but also
suggest what kind of model might work well in each new regime.  Of
particular interest would be the class of so-called \emph{hybrid
  systems}~\cite{hybrid}, which exhibit discrete transitions between
different continuous regimes---e.g., a lathe that has an intermittent
instability or traffic at an internet router, whose characteristic
normal traffic patterns shift radically during an attack.  Effective
modeling and prediction of these kinds of systems is quite difficult;
doing so adaptively and automatically---in the manner that is alluded
to at the end of the previous paragraph---would be an interesting
challenge.
